Taking Linear Logic Apart

### 2018-05-13 doc/tlla2018/main.tex
Fixed typing rules, removed possibility to continue after a (1) rule.

\hcp exhibits some behaviours which are impossible to directly translate back into \cp. For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
\[
  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
    \Gamma, \Delta, \tmty{x}{A \with B}}
\]
Instead, we define a new relation to characterise the relation between \hcp and \cp processes.
\begin{definition}\label{def:hcp-gk}
  The relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ is the congruence closure of the $\gamma$- and $\kappa$-rules for \hcp.
\end{definition}\noindent
This relation allows us to apply $\kappa$-rules under arbitrary prefixes. We can use this relation to rewrite any process to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
\begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
  If $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist $\seq[P_1]{\Gamma_1}, \dots, \seq[P_n]{\Gamma_n}$ in \cp, such that $\tm{P}\equiv_{\gamma\kappa}\tm{(\mtf{P_1}\ppar\dots\ppar\mtf{P_n})}$.
\end{lemma}\vspace*{-0.75\baselineskip}%
\begin{proof}
  We repeatedly apply the $\kappa{\ppar}$-rules to move the mixes upwards. There are three cases:
  \begin{enumerate*}[label={\alph*)}]
  \item
    if a mix gets stuck under a cut, it forms a \cp cut;
  \item
    if a mix gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
  \item
    otherwise, it moves all the way to the top.
  \end{enumerate*}
  Since the only way to continue after a $(\one)$ is by using a mix, all applications of $(\one)$ are now followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
\end{proof}\noindent

@@

%\section{Conclusions}
%\label{sec:conclusions}
%
%We introduced Hypersequent Classical Processes, a process calculus which addresses the mismatch between proof terms and \textpi-calculus terms which exists in Classical Processes~\citep{wadler2012}. We showed that \hcp enjoys preservation, progress and termination, and described its relation to \cp.

>>>>

\hcp exhibits some behaviours which are impossible to directly translate back into \cp. For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
\[
  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
    \Gamma, \Delta, \tmty{x}{A \with B}}
\]
Instead, we define a new relation to characterise the relation between \hcp and \cp processes.
\begin{definition}\label{def:hcp-gk}
  The relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ is the congruence closure of the $\gamma$- and $\kappa$-rules for \hcp.
\end{definition}\noindent
This relation allows us to apply $\kappa$-rules under arbitrary prefixes. We can use this relation to rewrite any process to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
\begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
  If $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist $\seq[P_1]{\Gamma_1}, \dots, \seq[P_n]{\Gamma_n}$ in \cp, such that $\tm{P}\equiv_{\gamma\kappa}\tm{(\mtf{P_1}\ppar\dots\ppar\mtf{P_n})}$.
\end{lemma}\vspace*{-0.75\baselineskip}%
\begin{proof}
  We repeatedly apply the $\kappa{\ppar}$-rules to move the mixes upwards. There are three cases:
  \begin{enumerate*}[label={\alph*)}]
  \item
    if a mix gets stuck under a cut, it forms a \cp cut;
  \item
    if a mix gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
  \item
    otherwise, it moves all the way to the top.
  \end{enumerate*}
  All applications of $(\one)$ are followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
\end{proof}\noindent

@@
